### 2022-11-23 ms.rmd
Add orchard plot
small update. orchard not working with complex model. grid issues so problems with emmeans

>>>>

orchard_plot(model1.3, mod = "trait_category",  group = "record_num",  data = lnRRQ10_data)

orchard_plot(model1.3, mod = "trait_category", at = list(type = c("acute", "acclim"), c_accl_time = 0, habitat = "m"), by = "type",  group = "record_num", weights = "prop", data = lnRRQ10_data, xlab = "lnRRQ10") 
```
